---
title: "Question 6"
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: null
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Ronan Morris
Ref1: Stellenbosch University
Email1: 22876634
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
---
```{r setup, include=FALSE}

rm(list = ls())

tinytex::install_tinytex(force = TRUE)
options(repos = "https://cran.mirror.ac.za/")

gc() 

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")

library(tidyverse)

library(fitHeavyTail)

```

In this question I was tasked to create a Global Balanced Index Fund portfolio using a mix of traded global indexes. Certain constraints were set to me by my superiors. I would like to discuss how I handled each. 

The first constraint was that it should be a "long only" strategy. In accordance with this, I set the lower bound to be equal to 1%. I set the upper bound to be 40%, which could seem excessive, I believe that "too much of a good thing" is a good mantra, and we should limit exposure to specific assets. An upper bound of 40% seems slightly high but it is not unheard of. 

I decided to use set the weighting for equities and bonds at 60% and 25% respectively. I have no particular research into the optimal weights of these instruments, and I do not believe that I could make a better allocation other than the limit. I will say that equities tend to have a higher volatility, but they yield a higher return (surprisingly so, actually - Mehra & Prescott, 1985). This allocation should be carefully considered in the real world, but I have simply set the constraints to the limit. 

I have not used any assets that do not have returns data for at least the last three years, and I have used quarterly re-balancing; this is in line with the policies of my superiors, and presumably the institution I would be working for in this scenario. I only considered data from 2010 onwards (after the financial crisis) for this analysis. The final consideration was what length to set the lookback period. I set it to 12 months, as I saw in much of the discussions online and in the literature, that this is a good starting point for portfolio optimisation. 

```{r Entire Portfolio Optimisation, include=FALSE, echo=FALSE}

rm(list = ls())

gc()

source('code/Impute_Missing_Returns.R') # This function is essentially from the practical offered by Nico. 

source('code/Optimisation_Function.R')

source('code/Roller_Function.R')

###

MAA <- read_rds("data/MAA.rds") %>% 
    select(-Name) %>% 
    arrange(date) %>% 
    rename(Tickers = Ticker) %>% 
    filter(date >= "2010-01-01")

msci <- read_rds("data/msci.rds") %>%
        filter(Name %in% c("MSCI_ACWI", 
                           "MSCI_USA", 
                           "MSCI_RE", 
                           "MSCI_Jap")) %>% 
        filter(date >= "2010-01-01") %>% 
        rename(Tickers = Name) %>% 
        arrange(date) 
    
# Here I am trying to separate and combine all the different asset classes mentioned in the question. 

Combined_assets <- rbind(MAA, msci) %>% 
    arrange(date)

CombAss3Yr <- Combined_assets %>% 
    group_by(Tickers) %>% 
    filter(date == as.Date("2018/01/01")) %>% 
    pull(Tickers) %>% 
    unique() # last three years
    
Start <- Combined_assets %>% 
    filter(Tickers %in% CombAss3Yr) %>% 
    group_by(Tickers) %>% 
    summarise(date = dplyr::first(date)) %>%
    summarise(latest = dplyr::first(date))

# Now I need to focus on getting the dates in order to perform re-balancing. 

DateVector <- Combined_assets %>% 
    filter(Tickers %in% CombAss3Yr) %>% 
    filter(date >= Start[[1]]) %>% 
    select(date) %>% 
    unique %>% 
    mutate(YM = format(date, "%Y%B")) %>% 
    group_by(YM) %>% 
    filter(date == dplyr::last(date)) %>% 
    ungroup() %>% 
    pull(date) %>% 
    unique

# But the re-balancing actually seems to be quarterly. 

DateVector # To get the first and last date!

QuarterDates <- rmsfuns::dateconverter(as.Date("2010-01-31"), 
                                       as.Date("2021-10-29"), 
                                       "weekdayEOQ") 

# Now that we have the necessary dates, and re balancing dates, we can filter the data appropriately and start seeing what sorts of returns we are getting. 

Combined_assets <- Combined_assets %>% 
    filter(Tickers %in% CombAss3Yr) %>% 
    filter(date >= Start[[1]]) %>% 
    filter(date %in% QuarterDates) %>% 
    group_by(Tickers) %>% 
    mutate(ret = Price/lag(Price) - 1) %>% 
    filter(date > dplyr::first(date)) %>% 
    select(-Price) %>%
    spread(Tickers, ret)

# I have not actually checked whether there are missing values, but just to be sure, I use the function from the tutorial.  

options(scipen = 999)

ReturnMatrix <- 
  impute_missing_returns(Combined_assets, 
  impute_returns_method = "Drawn_Distribution_Collective", 
  Seed = as.numeric(format( Sys.time(), "%Y%d%H%M")))

RetMatDateless <- data.matrix(ReturnMatrix[, -1])

# Constraints

LB = 0.01 # it is a long only portfolio
UB = 0.2 # do not want too much of a good thing 
Equities = 0.6 
Bonds = 0.25
meq = 1
Stonks <- ncol(RetMatDateless)

# Matrix 

BondMat <- rbind(matrix(0, 3, 6), -diag(6), matrix(0, 4, 6))

EquiMat <- rbind(matrix(0, nrow = 9, ncol = 4), -diag(4))

bvec <- c(1, rep(LB, Stonks), 
          -rep(UB, Stonks), 
          -rep(Equities, 4), 
          -rep(Bonds, 
               6))

Amat <- cbind(1, 
              diag(Stonks), 
              -diag(Stonks), 
              EquiMat, BondMat)

# Calculate optimal rolling weights for each type of portfolio optimization, which makes use of a function I created. 

PortfolioWeights <- 
QuarterDates %>% map_df(~Roller(ReturnMatrix, 
                                DateVector = ., 
                                Amat = Amat, 
                                bvec = bvec, 
                                LookBack = 12)) %>% 
    select(-Look_Back_Period)

```

Please see the first date of the optimised portfolio for all assets, their weights, and the method of optimisation. Namely, these include mean variance, minimum volatility, and the Sharpe portfolio. These have differing profiles. For example, one would want to drive for maximum diversification if assets have similar Sharpe ratios. The different types also make different assumptions about returns, or expected returns. 

```{r Display, include=TRUE, echo=FALSE}

head(PortfolioWeights, 15)

```

